### 2023-03-31 reachable-resilience.tex
Starting section 4 case Safe downward closed

\begin{proof}
% strong WSTS
% $\pred^*(I) = \pred^{k}(I)$
% Check all $k$ until $\pred^*(I) = \pred^{k}(I)$.
Since $\Safe=\uparrow \Safe$ and
$\mathscr{S}=(S,\rightarrow,\leq)$ is a WTSTS with strong %upward-
compatibility, then $\pred^n(\Safe)= \uparrow~\pred^n(\Safe)$ for all $n \in \N$,
and there exists $n_0 \in \N$ such that 
$\pred^{n_0}(\Safe) = \uparrow \pred^{n_0}(\Safe) = \uparrow \pred^*(\Safe) = \pred^*(\Safe)$.
We
\end{proof}

@@

\begin{corollary}
Bounded reachable-resilience and 
$k$ reachable-resilience are undecidable for strongly compatible WSTS with effective pred-basis.
\end{corollary}

\begin{proof} 
  From
  cf
the two  theorems above. 
\end{proof}

@@

>>>>

This undecidability result furthermore implies the undecidability of the other two state resilience problems by straightforward reductions.

@@

\begin{proof}
% strong WSTS
% $\pred^*(I) = \pred^{k}(I)$
% Check all $k$ until $\pred^*(I) = \pred^{k}(I)$.
Since $\Safe=\uparrow \Safe$ and
$\mathscr{S}=(S,\rightarrow,\leq)$ is a WTSTS with strong %upward-
compatibility, then $\pred^n(\Safe)= \uparrow~\pred^n(\Safe)$ for all $n \in \N$,
and there exists $n_0 \in \N$ such that 
$\pred^{n_0}(\Safe) = \uparrow \pred^{n_0}(\Safe) = \uparrow \pred^*(\Safe) = \pred^*(\Safe)$.
We compute 
$n_0$, then iteratively check whether $k$-state resilience hold for $k$ from $0$ to $n_0$.  
\end{proof}

\begin{corollary}
Bounded state-resilience and 
$k$ state-resilience are undecidable for strongly compatible WSTS with effective pred-basis.
\end{corollary}

\begin{proof} 
  From the two reductions above. 
\end{proof}

@@

The authors from \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}
have only been concerned with the case $\Safe = \uparrow \Safe$
and $\Bad =\downarrow \Bad$, however as mentioned in Section~3
the property for instance of mutual exclusion is often modelised with $\Safe = \downarrow \Safe$.
Hence it makes sense to consider this symmetrical case as well. \\

Undecidability in general: $\Safe = 0$, $\Bad = S \setminus 0$ ?

LOREM IPSUM \\

\begin{lemma}(Symmetrical from Lemma~\ref{Lemma intersection})\label{Lemma intersection 2}
Let $A \subseteq S$, $D \subseteq S$ be a downward-closed set and $U \subseteq S$ be an upward-closed set. 
Then $A \cap U \subseteq D$  iff $ (\downarrow  A) \cap U \subseteq D$.
\end{lemma}

\begin{proof}
Let us suppose that $A \cap U \subseteq D$. Then ${\downarrow (A \cap U)} \subseteq {\downarrow D} = D$.
Let us show that $({\downarrow A}) \cap U \subseteq {\downarrow (A \cap U)}$.
Let $x \in ({\downarrow A}) \cap U$, then there exists $a \in A$ such that $x \leq a$.
Since $x \in U$ and $U$ is downward-closed, we also have $a \in U$.
Hence $a \in A \cap U$ and then $x \in { \downarrow (A \cap U)}$.
In the other direction,
since $A \subseteq {\downarrow A}$, the inclusion
$({\downarrow  A}) \cap U \subseteq D$ implies
$A \cap U \subseteq ({\uparrow  A}) \cap U \subseteq D$.
\end{proof}

Lemma~\ref{Lemma intersection 2} can be used to show that
$\post^*(s) \cap \Bad \subseteq D$  iff $ (\downarrow  \post^*(s)) \cap \Bad \subseteq D$.

If, as in Section~XX, we have the \textcolor{red}{added hypothesis}
that
$\pred^*(\Safe)$ is downward closed this means that
$\post^*(s) \cap \Bad \subseteq \pred^*(\Safe)$  iff $ (\downarrow  \post^*(s)) \cap \Bad \subseteq \pred^*(\Safe)$.

And hence decidability follows.

\subsection{Other}

\mathieu{Everything below should be moved to the applications section no?}
